### 2019-05-16 manuscript/main.tex
Updates from Overleaf

Voluntary environmental governance faces further difficulties in new democracies. In Latin America, authoritarian regimes discouraged civil participation and reduced social capital, two necessary conditions for effective polycentric arrangements \citep{aligica2014institutional,ostrom1990governing}. Top-down climate policies also create incentives for organised groups to collude with state officials and pursue private interests. As a result, elites and state representatives have \textit{de facto} veto power over environmental legislation and can override local decisions to their own benefit.

>>>>

Voluntary environmental governance faces further difficulties in new democracies. In Latin America, authoritarian regimes discouraged civil participation and reduced social capital, two necessary conditions for effective polycentric arrangements \citep{aligica2014institutional,ostrom1990governing}. Top-down climate policies also create incentives for organised groups to collude with state officials and pursue private interests \citep{aklin2013understanding,aklin2014blames}. As a result, elites and state representatives have \textit{de facto} veto power over environmental legislation and can override local decisions to their own benefit.
